\LARGE How coexistence mechanisms mediate temporal stability

### 2016-02-25 manuscript/manuscript.Rmd
adds comparison plot to ms

>>>>

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/compare_plots.png}
  \caption{Relationship between resource variability ($\sigma_R$) and the coefficient of variation of total community biomass for both coexistence mechanisms. Each panel shows results from different levels of environmental cue correlations ($\rho$) for the storage effect; $\rho=1$ across all panels for relative nonlinearity results. On average, the storage effect leads to less variable biomass production through time.}
\end{figure}
